Vagueness and imprecise imitation in signaling games

### 2016-05-26 paper/version_final/paper.tex
Added authors academic addresses.

>>>>

\begin{flushright}
Michael Franke \\
Wilhelmstra\ss e 19 \\
Department of Linguistics \\
University of T\"ubingen \\
72072 T\"u bingen \\
Germany \\
\texttt{mchfranke@gmail.com} \\
\bigskip
Jos\'e Pedro Correia \\
Via Panorâmica s/n \\
Institute of Philosophy \\
Faculty of Arts \\
University of Porto \\
4150-564 Porto \\
Portugal \\
\texttt{zepedro.correia@gmail.com} \\
\end{flushright}
